%%
%%
%%Script from the short cut "Storia di Vendetta" made for Computer Animation at ESCOM.
%%This is a story of a man who lost everything and wants vengance.
%%Based in a real historical period of time with real characters who lived in the early XX century.
%%The Italian mob in the United States, better known as "La Cosa Nostra".
%%
%%By Ortiz Rodríguez Salvador Alejandro
%%Group: 3CV8
%%
%%

\documentclass{screenplay}[2020/03/26]
\title{Storia di Vendetta}
\author{Alex}
\address{555 George St NNW\\
Kaplan, ND 77777\\
999-999-9999}
\begin{document}
\coverpage

%% 1) Shows some action scenes with some dialogues that introduces the main plot of the story.
%%First Scene

\fadein
\extslug[midday/morning]{Rooftops}
The view goes down following the BAD GUYS while they're walking on
the street.
\\The BAD GUYS are talking
\begin{dialogue}[worried]{Salvatore D'Aquila}
I feel eyes on us!
\end{dialogue}
The view changes in different angles focusing on the BAD GUYS and SALVATORE DI ALESSANDRI watching them on the rooftops.
\\LUCKY LUCIANO is looking for the person whose following them arround the streets.
\\The other BAD GUYS get worried.
\begin{dialogue}[loudly]{Salvatore D'Aquila}
He could be here right now\dots And we wouldn't even know\dots
\end{dialogue}
SALVATORE DI ALESSANDRI shoots a gun and kills SALVATORE D'AQUILA, then the view switches in different angles and positions in a fast way, while SALVATORE DI ALESSANDRI appears killing the rest of the BAD GUYS, except for the only one who escapes, LUCKY LUCIANO.
\\The view becomes black.
\begin{dialogue}[screamming]{Someone}
Assassino!
\end{dialogue}

%% 2) Presents a little introduction of the story or the origins of the main character with his voice as the narrator.

\begin{dialogue}[narrating]{Salvatore Di Alessandri}
I did no choose this path.
\\It was chosen for me.
\end{dialogue}

%%Second Scene

\fadein
\extslug[midday]{Rooftops}
SALVATORE DI ALESSANDRI runnig over the rooftops wearing normal clothes with his friends.

%%Third Scene

\extslug[midday]{NY Streets}
SALVATORE DI ALESSANDRI pushing one of his friends while they are smiling.
\begin{dialogue}[excited]{Salvatore Di Alessandri}
Well boys! I think I'm the winner!
\end{dialogue}

%%Fourth Scene

\fadeout
\extslug[midday]{Highway}
SALVATORE DI ALESSANDRI driving his car in a race with his friends.
\begin{dialogue}[euphoric]{Salvatore Di Alessandri}
Faster! Faster! FASTER!
\end{dialogue}

\begin{dialogue}[narrating]{Salvatore Di Alessandri}
There are moments in life...
\end{dialogue}

%%Fifth Scene

\fadeout
\intslug[night]{dinning room}
SALVATORE DI ALESSANDRI is at the family dinner in a quiet scene. Everyone is laughing and seems to be happy.
\\CRISTINA is laughing while see ALFREDO speaking, GIOVANNI is eating, MARIA laughs quietly, while FRANCESCO and MARIO are laughing. SALVATORE is smiling while hi is holding a spoon.
\fadein

\begin{dialogue}[narrating]{Salvatore Di Alessandri}
That a man never forgets.
\end{dialogue}

SALVATORE DI ALESSANDRI is very happy and smiles a lot while is watching that scene.

%%Sixth Scene

\intslug[midday]{Living room}
SALVATORE DI ALESANDRI talking and laughing with his brothers on the couch.
SALVATORE smiles while hi is watching his brothers laughing.

%% Seventh Scene

\fadein
\extslug[morning]{streets}
SALVATORE DI ALESSANDRI is walking with FRANCESCO and MARIO.
\begin{dialogue}{Mario}
I think this is a goodlife my brothers.
\end{dialogue}
FRANCESCO smiles and looks at SALVATORE.
\begin{dialogue}[happy]{Francesco}
Yeah! It is... Don't you think so, little brother?
\end{dialogue}
SALVATORE smiles while FRANCESCO hughs him.
\begin{dialogue}[smiling]{Salvatore}
The best one, my brothers! The best one...
\end{dialogue}

%%Eighth Scene

\fadein
\extslug[afternoon]{streets}
SALVATORE DI ALESSANDRI is watching ELISSABETTA tottaly in love and smiling while she is talking to him.
\\They are walking on the streets holding hands.
\fadein

\begin{dialogue}[narrating]{Salvatore Di Alessandri}
His first kiss...
\end{dialogue}

%%Ninth Scene

\intslug[night]{bedroom}
SALVATORE and ELISSABETTA are kissing in a romantic dark scene.

\begin{dialogue}[narrating]{Salvatore Di Alessandri}
The first love...
\end{dialogue}

%%Tenth Scene

\fadeout
\extslug[midday/afternoon]{NY Streets}
SALVATORE DI ALESSANDRI and his friends are going to fight a gang in a street fight

\begin{dialogue}[narrating]{Salvatore Di Alessandri}
His first duel...
\end{dialogue}

%% 3) The main conflict or the purpose of the main character, included the appearance of the bad guys.
%%Eleventh Scene

\fadein
\extslug[afternoon]{NY Streets}
SALVATORE DI ALESSANDRI is getting sad while he is sitting down.

\begin{dialogue}[narrating]{Salvatore Di Alessandri}
But most of all\dots The moment when he discovers his purpose in life.
\end{dialogue}

%%Twelfth Scene

\fadeout
\extslug[night]{NY Streets}
While SALVATORE is being sad the scene gets darker and darker.

\begin{dialogue}[narrating]{Salvatore Di Alessandri}
For me that moment happened\dots Thirty years ago.
\end{dialogue}

%%thirteenth scene

\fadein
\extslug[day]{NY Streets}
GAETANO "TOMMY" REINA murders ALFREDO DI ALESSANDRI in a shooting on the streets of New York.

%%fourteenth scene

\fadeout
\extslug[day]{Highway}
MARIO, FRANCESCO and GIOVANNI DI ALESSANDRI are escaping in a car chase on the highway.
\\The cars corner them and starts shooting to their car until it explotes.

%%fifteenth scene

\fadein
\extslug[afternoon/night]{NY Streets}
SALVATORE DI ALESSANDRI looks his father's bloody body on the floor while is holding his hand and crying a lot.
\\SALVATORE D'AQUILA watches that scene afar in his vehicle.

\begin{dialogue}[out of his mind]{Salvatore Di Alessandri}
YOU'LL PAY FOR WHAT YOU HAVE DONE!
\end{dialogue}

SALVATORE D'AQUILA disappears into the distance.

\begin{dialogue}[narrating]{Salvatore Di Alessandri}
At first, I thought vengance would be easy.
\end{dialogue}

%% 4) The turning point of the story, when the main character becomes the person he was supposed to be
%%     and discovers his purpose
%%sixteenth scene

\fadein
\intslug[night]{Di Alessandri's House}
SALVATORE DI ALESSANDRI comes down the stairs, and enter to a secret room with a false door. Then SALVATORE enters a strange room full of artifacts and weapons.
\\He takes some clothes and starts dressing.

%%seventeenth scene

\fadeout
\extslug[day]{Streets}
SALVATORE DI ALESSANDRI is chasing SALVATORE D'AQUILA and his henchmen on the New York Streets, near a market.

%%eighteenth scene

\fadein
\intslug[night]{Di Alessandri's House}
SALVATORE DI ALESSANDRI takes a revolver and starts charging it. Then takes a shotgun and reload it.

\begin{dialogue}[narrating]{Salvatore Di Alessandri}
For thirty years I've lived in the shadows\dots
\end{dialogue}

%%nineteenth scene

\fadeout
\extslug[night]{Streets}
SALVATORE DI ALESSANDRI is envolved in a car chase. He takes out his hand of the window and starts shooting to another car whose is trying to escapes.
\\Then the other car explotes while SALVATORE is watching it.The fire illuminates Salvatore's serious face.

\begin{dialogue}[narrating]{Salvatore Di Alessandri}
Bringing death to those who deserved it.
\end{dialogue}

%%twentieth scene

\fadein
\intslug[night]{Di Alessandri's House}
SALVATORE DI ALESSANDRI adjusts a tie and puts on an elegant coat.

%%twentieth scene

\fadeout
\extslug[night]{Docks}
SALVATORE DI ALESSANDRI is in a gang shooting. He comes out of cover and shoots his shotgun killing GAETANO "TOMMY" REINA with a headshot. SALVATORE sees the moment when the dead body falls to the ground.

\begin{dialogue}[narrating]{Salvatore Di Alessandri}
I don't know who started this conspiracy.
\end{dialogue}

%%twenty-first scene

\fadein
\intslug[night]{Di Alessandri's House}
SALVATORE DI ALESSANDRI adjusts his hat while is looking himself in a mirror.
\\SALVATORE takes his rifle and comes out that room.

\begin{dialogue}[narrating]{Salvatore Di Alessandri}
But I know\dots who will end it.
\end{dialogue}

%%twenty-second scene

\fadeout
\extslug[day]{Streets}
SALVATORE DI ALESSANDRI is fighting with 2 guys at the same time, using some martial arts.

%%twenty-third scene

\fadein
\extslug[day]{Streets}
SALVATORE DI ALESSANDRI is fighting with 2 guys at the same time, using some martial arts.
\\SALVATORE disarm another guy and  knock him out using his own weapon.

%%twenty-fourth scene

\fadeout
\intslug[night]{Genovese's mansion}
In the middle of a party with many people we could see SALVATORE DI ALESSANDRI watching LUCKY LUCIANO talking to DON VITO GENOVESE between the crowd.

%%twenty-fifth scene

\fadein
\extslug[night]{Genovese's mansion rooftops}
SALVATORE DI ALESSANDRI is following and spying on LUCKY LUCIANO from the rooftops of the mansion.
\\DON VITO GENOVESE realizes the presence of SALVATORE DI ALESSANDRI and orders to capture him.
\\SALVATORE DI ALESSANDRI tries to escape.

\begin{dialogue}[explaining]{Don Vito Genovese}
Hi is Lucky Luciano, one of the most powerful men in all North America\dots And leader of the new mafia order.
\end{dialogue}

%%twenty-sixth scene

\fadein
\extslug[night]{Genovese's mansion garden}
DON VITO GENOVESE is talking to LUCKY LUCIANO in a secret gangster meeting while SALVATORE DI ALESSANDRI is hidden in the shadows.
\\LUCKY LUCIANO is watching the other gangsters.

%%twenty-seventh scene

\fadeout
\extslug[morning]{NY City canals}
LUCKY LUCIANO kills one man from behind.

%%twenty eighth scene

\fadein
\extslug[day]{NY Streets}
LUCKY LUCIANO is paying money to JOE PROFACI and closing business.
\\SALVATORE DI ALESSANDRI appears in the distance in a car. 

%%twenty-ninth scene

\fadeout
\extslug[night]{NY Streets}
SALVATORE DI ALESSANDRI is in a car chase involved in a shooting.

%%thirtieth scene

\fadein
\extslug[afternoon]{NY Streets}
SALVATORE DI ALESSANDRI is shooting to some gangsters from the roofs with his rifle.
\\Then SALVATORE is fighting hand to hand with some gangsters on the streets.

%%thirty-first scene

\fadeout
\extslug[night]{NY Streets}
SALVATORE DI ALESSANDRI is escaping of the cops in a car chase.

%%thirty second scene

\fadein
\extslug[afternoon]{Docks}
SALVATORE DI ALESSANDRI fights violently with a man.
\\That scene cuts in the moment when SALVATORE shoots his rifle to his enemy's head.
\\The scene becomes dark.

\begin{dialogue}[narrating]{Salvatore Di Alessandri}
My name is Salvatore Di Alessandri\dots And like my father before me\dots I am\dots
\end{dialogue}

%%thirty-third scene

\fadein
\extslug[afternoon]{Outside Alessandri's House}
SALVATORE DI ALESSANDRI is smoking while adjusts his hat and coat. He reload his weapon and get in his car.

\begin{dialogue}[narrating]{Salvatore Di Alessandri}
One of them.
\end{dialogue}

%% 5) End Credits

\end{document}
%% 
%% 
%%
%%End of the Script
%% End of file `StoriaDiVendetta.tex'.
